The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes

### 2023-04-06 hw1/paper/main.tex
update PLA related work

\author{Hsieh Cheng-Han}
\date{October 2022}
\maketitle

@@

@@

  \bf{perceptron learning algorithm (PLA)}:

@@

@@

\section{PLA}

>>>>

\author{Hsieh Cheng-Han, Hsu Ting Hao, Sun Shih Yu}
\date{April 2023}
\maketitle

@@

  \bf{perceptron learning algorithm (PLA)}: \rm{Perceptron} learning algorithm \cite{gallant1990perceptron} is proposed by Gallant 
  in 1990, which is a fast and simple classification algorithm. However, the limitation of perceptron learning algorithm is that it 
  can only address the data which is linear separable. Thus, the following model connecting layers of perceptrons is proposed:

@@

@@

\section{PLA}
  Assume that in a dataset $D$, there are two class labels. A perceptron will determine a data point with unknown class label by formula 
  \begin{equation}
    \rm{sign}(w^Tx)
  \end{equation}
  where $w$ is

@@
